\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.75]{geometry}

\name{Pratik}{Fandade}
\phone[mobile]{7163398155}
\email{pfandade@buffalo.edu}

\begin{document}

\recipient{To}{Hiring Committee, \\ University at Buffalo \\ Buffalo, NY}
\date{\today}
\opening{Dear Hiring Committee,}
\closing{Sincerely,}
\makelettertitle

I am writing to express my strong interest in a Full Stack / Software Engineer role at your organization. With over three years of experience building and scaling production systems at Colgate-Palmolive and a current Master’s in Computer Science and Engineering at the University at Buffalo (expected December 2025), this background combines hands-on industry impact with advanced academic training that aligns well with modern software engineering teams.

In my recent role as a Software Engineer at Colgate-Palmolive, I collaborated with a global team of 16 developers to build and maintain proprietary inventory planning software used by over 10,000 businesses worldwide. I developed APIs using Django, React, GCP, Kubernetes, RabbitMQ, Docker, and Celery that supported over 1 million concurrent I/Os with low latency, and improved strategic business logic implementations that delivered 50\% time savings and increased operational efficiency. I was also recognized for optimizing front-end architecture and reducing technical overhead by 30\%, leading to a promotion to Software Engineer after just one year.

Previously, as a Junior Software Engineer and Intern at Colgate-Palmolive, I refactored complex front-end architectures with React, Redux, Ag-Grid, Ant Design, and MUI-X to reduce performance overhead by 70\% and enhance data visualization for critical business workflows. Through test-driven development and tooling such as Jest, Cypress, and GitHub Actions, I resolved 100+ bugs and feature requests and reduced build times by 60\%, significantly improving reliability and collaboration across distributed teams. Beyond my industry experience, I have engineered a Redis-inspired in-memory database in Go that reduced application response time by 30\% and maintained 99.99\% uptime via master–replica synchronization, and built an LSTM-based stock prediction system with 91.96\% accuracy using live Yahoo Finance data and Twitter sentiment analysis.

I am excited to bring this blend of full-stack development, distributed systems, and performance optimization experience to a team that values scalable architecture, reliable delivery, and measurable business impact. My background in languages such as JavaScript, TypeScript, Python, Go, and Rust, combined with experience across PostgreSQL, MySQL, MongoDB, Docker, Kubernetes, and cloud platforms, positions me to contribute quickly to modern microservice and data-intensive environments. I would welcome the opportunity to discuss how this experience can support your engineering roadmap and help deliver robust, high-impact software for your customers.

\makeletterclosing

\end{document}

