%-------------------------
% Resume in Latex
% Author : Pratik Fandade
%------------------------

\documentclass[letterpaper,9pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=Black]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-0pt}
\input{glyphtounicode}
\setlist[itemize]{left=0pt, label=\textbullet, itemsep=0.5pt, topsep=0.5pt}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.4in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\normalsize\bfseries
}{}{0em}{}[\color{black}\titlerule]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1}
  }
}

\newcommand{\classesList}[4]{
  \item{
    {#1 #2 #3 #4}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textit{#2} \\
      \textit{#3} & \textbf{#4}
    \end{tabular*}
}

\newcommand{\resumeExheading}[2]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textbf{#2}
    \end{tabular*}
}


\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textbf{#2}
    \end{tabular*}
}

\newcommand{\resumeEdSubheading}[5]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textit{#2}
      \textit{#3} & \textbf{#4}
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemi{$\vcenter{\hbox{$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\small
%----------HEADING----------
\begin{center}
  \textbf{\huge \scshape Pratik Fandade} \\
  \href{tel:+1-716-339-8155}{716-339-8155} $|$
  \href{mailto:fandadep6@gmail.com}{fandadep6@gmail.com} $|$
  Buffalo, NY $|$
  \href{https://linkedin.com/in/pratikfandade}{\underline{Linkedin}} $|$
  \href{https://github.com/prkbuilds}{\underline{Github}} $|$
  % {\huge \scshape Ok Confusion} \\  ~
  % \href{tel:+}{\underline{(XXX) XXX-XXXX}} $|$
  % \href{mailto:}{\underline{johndoe@gmail.com}} $|$
  % xxxxxxx, NY \\
  % \href{https://}{\underline{linkedin.com/in/johndoe}} $|$
  % \href{https://}{\underline{github.com/johndoe}} $|$
  % \href{https://}{\underline{leetcode.com/u/johndoe}}
\end{center}
%-------------SUMMARY------------
\vspace{-10pt}
\section{SUMMARY}
Data Engineer with 3+ years of experience building backend systems and data-intensive services, with a strong foundation in databases, distributed systems, and cloud infrastructure. Proven experience designing data pipelines, optimizing storage and query performance, and operating reliable systems at scale. MS in Computer Science and Engineering from SUNY Buffalo. Actively applying for data engineering roles in 2025.
%-----------EXPERIENCE-----------
\vspace{-10pt}
\section{EXPERIENCE}
\resumeSubHeadingListStart
  \resumeExheading{\textbf{Redprint} - Software Developer Intern}{Jun 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Built data ingestion pipelines using Go services to collect application events and API data, persisting structured records to cloud-backed storage on AWS, supporting analytics for 1,000+ active users.}
    \resumeItem{Reduced end-to-end data availability latency by 35\% by optimizing API ingestion paths, adding database indexing, and tuning query plans for read-heavy analytical workloads.}
    \resumeItem{Designed schemas and storage patterns for user and event data, improving query performance and enabling downstream reporting with consistent data freshness.}
    \resumeItem{Deployed containerized data services on AWS (EC2, S3) with automated CI/CD pipelines via GitHub Actions, achieving zero-downtime pipeline updates.}
    \resumeItem{Implemented monitoring for ingestion jobs and backend services, improving pipeline reliability and reducing incident response time.}
  \resumeItemListEnd
  \vspace{0.5em}
  \resumeExheading{\textbf{Colgate Palmolive} - Software Engineer}{Aug 2022 -- Aug 2024}
  \resumeItemListStart
    \resumeItem{Designed and maintained batch-style data pipelines using Django, PostgreSQL, and RabbitMQ to ingest, transform, and serve operational data for internal analytics systems handling 1M+ records per day.}
    \resumeItem{Improved analytical query throughput by 70\% by optimizing SQL queries, introducing caching strategies, and tuning PostgreSQL indexes and partitions.}
    \resumeItem{Built distributed data-processing services using RabbitMQ for event-driven ingestion, enabling near-real-time propagation of business events into reporting stores.}
    \resumeItem{Modeled relational schemas to support reporting and downstream consumption, reducing query latency to sub-100ms for frequently accessed aggregates.}
    \resumeItem{Implemented CI/CD pipelines with Docker and GitHub Actions to validate data-processing logic and schema changes, reducing pipeline-related production issues by 60\%.}
    \resumeItem{Deployed and operated data services on GCP, ensuring high availability and consistent data delivery under peak load.}
  \resumeItemListEnd
  \vspace{0.5em}
  \resumeExheading{\textbf{Colgate Palmolive} - Software Engineering Intern}{Feb 2022 -- Aug 2022}
  \resumeItemListStart
    \resumeItem{Assisted in building ETL-style workflows that extracted application data from PostgreSQL, applied transformations in backend services, and loaded results into reporting tables.}
    \resumeItem{Improved data pipeline reliability and release velocity by 30\% by introducing automated CI/CD workflows with test coverage for data-related logic.}
    \resumeItem{Refactored backend components to reduce redundant reads and improve data access efficiency, contributing to faster downstream analytics queries.}
    % \resumeItem{Collaborated with backend and QA teams to ship tested, containerized services to GCP environments.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\vspace{-10pt}
\section{SKILLS}
\resumeItemListStart
  \resumeItem{\textbf{Data Engineering \& Processing:} ETL/ELT, Batch Processing, Stream Processing, Python ETL, Kafka, RabbitMQ, gRPC-based Services, Data Modeling, Data Quality, Schema Evolution}
  \resumeItem{\textbf{Databases \& Storage:} PostgreSQL, MySQL, Redis, BigQuery, S3, GCS, Relational Modeling, Indexing, Partitioning, Columnar Formats (Parquet)}
  \resumeItem{\textbf{Cloud \& DevOps:} AWS (EC2, S3), GCP (BigQuery, GCS), Docker, Kubernetes, Terraform, CI/CD, Prometheus, Grafana}
\resumeItemListEnd
%-----------PROJECTS-----------
\vspace{-10pt}
\section{PROJECTS}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{Production-Style Event Analytics Pipeline} $|$ \textit{Python, Kafka, Spark, PostgreSQL, Parquet, Docker, GCP}}{}
  \resumeItemListStart
    \resumeItem{Designed an end-to-end data pipeline ingesting application events from Kafka, processing them with Spark, and storing curated datasets in PostgreSQL and Parquet-backed tables.}
    \resumeItem{Implemented deduplication, schema validation, and idempotent writes, ensuring accurate analytics over millions of event records.}
    \resumeItem{Partitioned data by time and event type, reducing analytical query latency by 40\% and improving data freshness SLAs.}
    \resumeItem{Exposed aggregated datasets for dashboard consumption and ad-hoc SQL analysis.}
  \resumeItemListEnd
  \vspace{0.5em}
  % \resumeProjectHeading{\textbf{Custom Linux Process Monitor} $|$ \textit{C, eBPF, Prometheus, Grafana}}{}
  % \resumeItemListStart
  %   \resumeItem{Enabled \textbf{real-time kernel metric} visibility as measured by Prometheus scrape latency using a low-overhead eBPF tracing tool.}
  %   \resumeItem{Delivered continuous system monitoring as measured by live dashboards by integrating \textbf{Grafana} visualizations.}
  % \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\vspace{-10pt}
\section{EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading{\textbf{University at Buffalo, State University of New York}}{Buffalo, NY}
  {Master of Science in Computer Science and Engineering}{Aug 2024 -- Dec 2025}
  \resumeSubheading{\textbf{Vishwakarma Institute of Technology, Pune}}{Pune, Maharashtra}
  {Bachelor of Technology in Information Technology}{Aug 2018 -- Aug 2022}
\resumeSubHeadingListEnd
%--------PUBLICATIONS/ACHIEVEMENTS--------
% \vspace{-10pt}
% \section{OPEN SOURCE, PUBLICATIONS \& CERTIFICATIONS}
% \resumeItemListStart
%   \resumeItem{Improved Diesel ORM query performance by optimizing connection pooling, contributing to an \textbf{Open-Source library (Rust)} as a contributor and reviewer.}
%   \resumeItem{Published research achieving 90\% stock trend prediction accuracy as measured by test datasets by combining time-series modeling and sentiment analysis.}
%   \resumeItem{Increased crypto platform reliability by 35\% as measured by uptime logs by optimizing Rust backend, RabbitMQ messaging, and PostgreSQL}
%   \resumeItem{Completed 10+ \textbf{Google Cloud Qwiklabs} as measured by earned credentials, covering GKE, Docker, Terraform, BigQuery, and CI/CD.}
% \resumeItemListEnd

\end{document}
