%-------------------------
% Resume in Latex
% Author : Pratik Fandade
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=Black]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage[T1]{fontenc}  % Enables bold small caps via European encoding [web:2]
\usepackage{lmodern}      % Latin Modern provides more font shapes [web:2]
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-0pt}
\input{glyphtounicode}
\setlist[itemize]{left=0pt, label=\textbullet, itemsep=0.5pt, topsep=0.5pt}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.4in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\normalsize\bfseries
}{}{0em}{}[\color{black}\titlerule]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1}
  }
}

\newcommand{\classesList}[4]{
  \item{
    {#1 #2 #3 #4}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize#1} & \textit{#2} \\
      \textit{#3} & \textbf{#4}
    \end{tabular*}
}

\newcommand{\resumeExheading}[2]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textbf{#2}
    \end{tabular*}
}


\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textbf{#2}
    \end{tabular*}
}

\newcommand{\resumeEdSubheading}[5]{
  \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize#1} & \textit{#2}
      \textit{#3} & \textbf{#4}
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemi{$\vcenter{\hbox{$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\small
%----------HEADING----------
\begin{center}
  \textbf{\huge \scshape Pratik Fandade} \\
  \href{tel:+1-716-339-8155}{716-339-8155} $|$
  \underline{\href{mailto:fandadep6@gmail.com}{fandadep6@gmail.com}} $|$
  % United States $|$
  \href{https://linkedin.com/in/pratikfandade}{\underline{linkedin.com/in/pratikfandade}} $|$
  \href{https://github.com/prkbuilds}{\underline{github.com/prkbuilds}} $|$
\end{center}
\vspace{-6pt}
%-------PROGRAMMING SKILLS-------
\vspace{-12pt}
\section{SKILLS}
\resumeItemListStart
  \resumeItem{\textbf{Programming:} C, C++, Python, Rust, Go, Bash | \textbf{Data \& Storage:} PostgreSQL, Redis, SQL, BigQuery}
  \resumeItem{\textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, RabbitMQ, Kafka, Flink, Kubernetes (Gardener), Terraform}
  \resumeItem{\textbf{Backend \& Systems:} Distributed Systems, REST, gRPC, Async Jobs, Caching, Concurrency(Threads/Synchronization)}
  \resumeItem{\textbf{Reliability \& Quality:} OpenTelemetry, Grafana, WatchDog, Prometheus, Logging, Metrics, Monitoring}
\resumeItemListEnd
%-----------EXPERIENCE-----------
\vspace{-12pt}
\section{EXPERIENCE}
\resumeSubHeadingListStart
  \resumeSubheading{Redprint}{New York, US}{Software Engineer}{Jun 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Improved API reliability by reducing error rate from 1.2\% to \textbf{0.2\%} by adding \textbf{OpenTelemetry} tracing + structured logging, request tracing/correlation IDs, and SLO-based alerting (latency/error rate/saturation) on critical endpoints.}
    \resumeItem{Cut \textbf{MTTR} from 75 min to 20 min by building \textbf{Grafana} dashboards latency, queue depth, worker failures, DB health) and writing runbooks for top incident patterns.}
    \resumeItem{Reduced bulk-write time from 45s to \textbf{3s} by converting row-by-row updates to \textbf{set-based Postgres} operations, batching, and transaction scoping to minimize lock contention}
    \resumeItem{Scaled from 3k to \textbf{15k DAU} by tuning autoscaling, right-sizing compute, and caching hot reads; maintained stable tail latency during peak traffic.}
    \resumeItem{Reduced production regressions by \textbf{60\%} by introducing health checks, graceful shutdown, canary rollouts, and automated smoke tests in the deployment pipeline}
  \resumeItemListEnd
  \resumeSubheading{Colgate Palmolive}{Mumbai, India}{Software Engineer}{Feb 2022 -- Aug 2024}
  \resumeItemListStart
    \resumeItem{Shipped a bulk-edit engine that updated \textbf{100,000+ rows} in \textasciitilde1s (previously 30s) by using \textbf{set-based postgres updates}, batching, and async recomputation with \textbf{RabbitMQ} workers on \textbf{Kubernetes}.}
    \resumeItem{Improved async throughput \textbf{3x} and reduced peak backlog \textbf{78\%} by splitting hot/cold queues, tuning worker concurrency/prefetch, and implementing retries + DLQ with idempotent handlers.}
    \resumeItem{Reduced p95 API latency from \textbf{\textasciitilde800ms to \textasciitilde150ms} by adding indexes, rewriting expensive queries, and moving recomputation off the request path into async jobs.}
    \resumeItem{Increased peak worker scalability from \textbf{\textasciitilde30 to \textasciitilde100} concurrent workers during planning windows by tuning kubernetes autoscaling and right-sizing cpu/memory requests/limits.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\vspace{-12pt}
\section{PROJECTS}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{TacoDB} $|$ \textit{C++, SQL, Storage Engine, Buffer Manager}}{}
  \resumeItemListStart
    \resumeItem{Built a lightweight relational database with a disk-backed storage engine, buffer pool, and write-ahead logging to ensure durability and crash recovery.}
    \resumeItem{Implemented concurrency and correctness primitives (locking/latches, transactions) and optimized I/O paths via page caching, eviction policy tuning, and structured performance profiling.}
    \resumeItem{Designed query execution and planning with a cost-based optimizer and operators (scan/join/aggregate), focusing on predictable latency under large datasets.}
  \resumeItemListEnd
  \resumeProjectHeading{\textbf{Distributed Raft-based Redis} $|$ \textit{Go, gRPC, Raft, Docker}}{}
  \resumeItemListStart
  \resumeItem{Engineered a fault-tolerant, replicated KV store using Raft (leader election, log replication, snapshots) to provide consistency and automated failover under node loss.}
  \resumeItem{Hardened the system for production-like conditions by adding idempotent request handling, timeouts/retries, backpressure, and metrics for p95 latency, replication lag, and leader churn.}
  \resumeItem{Containerized and orchestrated multi-node clusters with Docker for repeatable deployments; built failure-injection tests (partition/kill/restart) to validate recovery guarantees.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\vspace{-12pt}
\section{EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading{\textbf{University at Buffalo, State University of New York (SUNY)}}{Buffalo, NY}
  {Master of Science in Computer Science and Engineering}{Aug 2024 -- Dec 2025}
  \resumeSubheading{\textbf{Vishwakarma Institute of Technology, Pune}}{Pune, Maharashtra}
  {Bachelor of Technology in Information Technology}{Aug 2018 -- Aug 2022}
\resumeSubHeadingListEnd
%--------PUBLICATIONS/ACHIEVEMENTS--------
\vspace{-12pt}
\section{OPEN SOURCE, PUBLICATIONS \& CERTIFICATIONS}
\resumeItemListStart
  \resumeItem{Improved Diesel ORM query performance by optimizing connection pooling, contributing to an \textbf{Open-Source library (Rust)} as a contributor and reviewer.}
  \resumeItem{Published research achieving 90\% stock trend prediction accuracy as measured by test datasets by combining time-series modeling and sentiment analysis.}
  \resumeItem{Completed 10+ \textbf{Google Cloud Qwiklabs} covering GKE, Docker, Terraform, BigQuery, and CI/CD.}
\resumeItemListEnd

\end{document}
